Synthesizing Quotient Lenses

### 2018-02-26 papers/QuotientLenses/main.tex
checkpoint

This section introduces Quotient Regular Expressions or QREs. QREs are regular
expressions augmented with syntax that lets them simultaneously express a
language and how to convert from that language into its canonical elements.

\subsection{Syntax of Quotient Regular Expressions}
The language of Quotient Regular Expressions (QREs) is given by the following
grammar:
\begin{align*}
c := \; &R \sep \project{R}{s} \sep \squash{c}{c'}{f} \sep
\perm{c_1, \ldots, c_n}{c} \\
& | \; \normalize{R}{R'}{f} \sep c \semicolon c' \sep c \cdot c''' \sep (c \sep
c') \sep c^*,
\end{align*}
where $c$ ranges over QREs, $R$ ranges over regular expressions, $f$ ranges over
functions between regular languages, and $s$ ranges over character strings. In
the following sections, we will use the the notation $\mathcal{L}(R)$ to mean
the language accepted by the regular expression $R$.

>>>>

Quotient Regular Expressions allow programs to specify a regular language,
an equivalence relation over elements of the language and a function to convert
elements of the language into normal form.

\subsection{Syntax}

The language of Quotient Regular Expressions (QREs) is given by the following
grammar:
\begin{align*}
c := \; &R \sep \project{R}{s} \sep \squash{c}{c'}{f} \sep
\perm{c_1, \ldots, c_n}{c} \\
& | \; \normalize{R}{R'}{f} \sep c \semicolon c' \sep c \cdot c''' \sep (c \sep
c') \sep c^*,
\end{align*}
where $c$ ranges over QREs, $R$ ranges over regular expressions, $f$ ranges over
functions between regular languages, and $s$ ranges over character strings.
$\mathcal{L}(R)$ is
the language accepted by the regular expression $R$.

Section~\ref{subsec:qre-expressions} presented a number of examples
